---
title: "lcrtcolorsr Examples"
author: "Brian Froeb"
date: "5/12/2023"
output: html_document
---
```{r echo=FALSE}
library(ggplot2)
library(tmap)
library(lcrtcolorsr)
data(NLD_muni)
```
# Exmaples {.tabset}

## Scale Color Examples

### Discrete Palettes
```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_lcrt(palette = "logo")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_lcrt(palette = "lines")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_lcrt(palette = "cool_to_warm")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_lcrt(palette = "cold_to_hot")
```

### Continuous Palettes
```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_lcrt(discrete = FALSE, palette = "Coral_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_lcrt(discrete = FALSE, palette = "Orange_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_lcrt(discrete = FALSE, palette = "Yellow_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_lcrt(discrete = FALSE, palette = "Green_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_lcrt(discrete = FALSE, palette = "Aqua_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_lcrt(discrete = FALSE, palette = "Blue_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_lcrt(discrete = FALSE, palette = "Purple_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_lcrt(discrete = FALSE, palette = "Pink_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_lcrt(discrete = FALSE, palette = "cool_to_warm")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_lcrt(discrete = FALSE, palette = "cold_to_hot")
```

## Scale Fill Examples

### Discrete Palettes
```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_lcrt(palette = "logo", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_lcrt(palette = "lines", guide = "none")
```


```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_lcrt(palette = "Coral_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_lcrt(palette = "Orange_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_lcrt(palette = "Yellow_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_lcrt(palette = "Green_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_lcrt(palette = "Aqua_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_lcrt(palette = "Blue_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_lcrt(palette = "Purple_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_lcrt(palette = "Pink_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_lcrt(palette = "cool_to_warm", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_lcrt(palette = "cold_to_hot", guide = "none")
```

## Geographic Data with ggplot2

These palettes can also be used with ggplot2 to display geographic data with both continuous and discrete scales, uses the scale fill function.

### Discrete Palettes
```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = province)) +
  scale_fill_lcrt(palette = "logo")
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = province)) +
  scale_fill_lcrt(palette = "lines")
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = province)) +
  scale_fill_lcrt(palette = "cool_to_warm")
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = province)) +
  scale_fill_lcrt(palette = "cold_to_hot")
```

### Continous Palettes
```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_lcrt(palette = "Coral_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_lcrt(palette = "Orange_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_lcrt(palette = "Yellow_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_lcrt(palette = "Green_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_lcrt(palette = "Aqua_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_lcrt(palette = "Blue_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_lcrt(palette = "Purple_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_lcrt(palette = "Pink_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_lcrt(palette = "cool_to_warm", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_lcrt(palette = "cold_to_hot", discrete = FALSE)
```

## Geographic Data with tmap

tmap uses a differing syntax from ggplot however by using the lcrt_color_pal function, with a step count indicated, and saving the output to an object these palettes can be used in tmap.

### Discrete Palettes
```{r}
MyPal <- lcrt_color_pal("logo")(10)
tm_shape(NLD_muni) +
  tm_polygons("province", palette = MyPal) 
```

```{r}
MyPal <- lcrt_color_pal("lines")(10)
tm_shape(NLD_muni) +
  tm_polygons("province", palette = MyPal) 
```

```{r}
MyPal <- lcrt_color_pal("cool_to_warm")(10)
tm_shape(NLD_muni) +
  tm_polygons("province", palette = MyPal)
```

```{r}
MyPal <- lcrt_color_pal("cold_to_hot")(10)
tm_shape(NLD_muni) +
  tm_polygons("province", palette = MyPal)
```

### Continous Palettes
```{r}
MyPal <- lcrt_color_pal("Coral_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```

```{r}
MyPal <- lcrt_color_pal("Orange_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```

```{r}
MyPal <- lcrt_color_pal("Yellow_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```

```{r}
MyPal <- lcrt_color_pal("Green_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- lcrt_color_pal("Aqua_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```

```{r}
MyPal <- lcrt_color_pal("Blue_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- lcrt_color_pal("Purple_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- lcrt_color_pal("Pink_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```

```{r}
MyPal <- lcrt_color_pal("cool_to_warm")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- lcrt_color_pal("cold_to_hot")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```
