---
title: "lcrtcolorsr Examples"
author: "Brian Froeb"
date: "5/12/2023"
output: html_document
editor_options: 
  chunk_output_type: inline
---
```{r echo=FALSE}
library(ggplot2)
library(tmap)
library(lcrtcolorsr)
data(NLD_muni)
```

There are currently 71 colors included in this package the color names and their hex codes are below
```{r, echo=FALSE}
lcrt_color_list
```

These are grouped into 20 color palettes, the colors included in each palette and their hex codes are below
```{r, echo=FALSE}
lcrt_color_palettes
```

These color palettes can be inserted into ggplot graphics, examples of each palettes in ggplot are below

## Functions Included

This package includes four functions:

- lcrt_cols()
- lcrt_color_pal()
- scale_color_lcrt()
- scale_fill_lcrt()

#### lcrt_cols
takes a input string or group of strings and returns the hex code. 
The color must be one of the colors included in this package

##### Example:
```{r}
lcrt_cols("Ocean")

lcrt_cols("Sand", "Purple")
```

#### lcrt_color_pal

Converts an input string representing a color palette into a function that can be converted into a usable color palette.

```{r}
lcrt_color_pal("cool_to_warm")
```

By adding a step count after the function it will return a usable palette

```{r}
lcrt_color_pal("cool_to_warm")(10)
```

These palettes can be reversed as needed

```{r}
lcrt_color_pal("cool_to_warm", reverse = TRUE)(10)
```

#### scale_color_lcrt and scale_fill_lcrt

These functions supply a fill or color to a ggplot call. See examples below.

